### 2016-01-18 paper.tex
Add load cell capacity

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The blockage ratio based on the rotor
frontal and tank cross-sectional area was 10\%. The turbine was mounted in a
frame built from NACA 0020 struts, attached to the tow carriage by four linear
bearings, which transfer all streamwise force to a pair of Sentran ZB S-beam
load cells \cite{SentranZB}. The turbine shaft RPM was controlled by a servo
motor system, which allowed precise control of the turbine tip speed ratio. The
load torque was measured by an Interface T8 200 Nm capacity inline rotary torque
transducer \cite{InterfaceT8}. An additional Sentran ZB load cell mounted at a
fixed distance from the servo motor via a moment arm provided a redundant torque
measurement. Turbine shaft angle was measured using the Kollmorgen AKD servo
drive's emulated encoder output \cite{KollmorgenAKD}, set to $10^5$ counts per
turbine shaft revolution. Carriage speed, and therefore inflow velocity was
measured using a Renishaw LM15 linear encoder with 10 $\mu$m resolution
\cite{RenishawLM15}. All of these performance-related quantities were sampled at
2 kHz, while the tow tank's motion controller provided redundant measurements of
the carriage speed turbine angular velocity sampled at 1 kHz. Turbine wake
measurements at 1 meter downstream were measured with a Nortek Vectrino+
acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200 Hz. A photo
and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.

>>>>

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Fig.~\ref{fig:exp-setup}. The blockage ratio based on the rotor
frontal and tank cross-sectional area was 10\%. The turbine was mounted in a
frame built from NACA 0020 struts, attached to the tow carriage by four linear
bearings, which transfer all streamwise force to a pair of 500 lbf capacity
Sentran ZB S-beam load cells \cite{SentranZB}. The turbine shaft RPM was
controlled by a servo motor system, which allowed precise control of the turbine
tip speed ratio. The load torque was measured by an Interface T8 200 Nm capacity
inline rotary torque transducer \cite{InterfaceT8}. An additional Sentran ZB
load cell mounted at a fixed distance from the servo motor via a moment arm
provided a redundant torque measurement. Turbine shaft angle was measured using
the Kollmorgen AKD servo drive's emulated encoder output \cite{KollmorgenAKD},
set to $10^5$ counts per turbine shaft revolution. Carriage speed, and therefore
inflow velocity was measured using a Renishaw LM15 linear encoder with 10 $\mu$m
resolution \cite{RenishawLM15}. All of these performance-related quantities were
sampled at 2 kHz, while the tow tank's motion controller provided redundant
measurements of the carriage speed turbine angular velocity sampled at 1 kHz.
Turbine wake measurements at 1 meter downstream were measured with a Nortek
Vectrino+ acoustic Doppler velocimeter \cite{NortekVectrino}, sampling at 200
Hz. A photo and drawing of the experimental setup are shown in
Fig.~\ref{fig:exp-setup-photo} and Fig.~\ref{fig:exp-setup}, respectively.
